Incentivizing Exploration with Unbiased History

### 2018-11-02 main.tex
Added explanation of unbiased to the abstract.

In this paper, we study a particular class of disclosure policies that use messages, called {\em unbiased subhistories}, consisting of the actions and rewards chosen by a subsequence of past agents.  One trivial message of this form contains the full history; a disclosure policy that chooses to use such messages risks inducing herding behavior among the agents and thus has regret linear in the number of rounds.  Our main result is a disclosure policy using unbiased subhistories that obtains regret $\tilde{O}(\sqrt{T})$.  We also exhibit simpler policies with higher, but still sublinear, regret.  These policies can be interpreted as dividing a sublinear number of agents into constant-sized focus groups, whose histories are then fed to future agents.
\end{abstract}
\end{titlepage}

>>>>

In this paper, we study a particular class of disclosure policies that use messages, called {\em unbiased subhistories}, consisting of the actions and rewards from by a subsequence of past agents, where the subsequence is chosen ahead of time.  One trivial message of this form contains the full history; a disclosure policy that chooses to use such messages risks inducing herding behavior among the agents and thus has regret linear in the number of rounds.  Our main result is a disclosure policy using unbiased subhistories that obtains regret $\tilde{O}(\sqrt{T})$.  We also exhibit simpler policies with higher, but still sublinear, regret.  These policies can be interpreted as dividing a sublinear number of agents into constant-sized focus groups, whose histories are then fed to future agents.
\end{abstract}
\end{titlepage}
